\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\input{glyphtounicode}

\usepackage[default]{sourcesanspro}
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}


\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\centering
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]


\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-3pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

  %-----------HEADING-----------
  \begin{center}
      {\large Jason Zhang} \\ 
      \begin{multicols}{2}
          \begin{flushleft}
              \href{mailto:jiajunzh@uw.edu}{jiajunzh@uw.edu}\\
              \href{tel:+14258983210}{425-898-3210}
          \end{flushleft}
          \begin{flushright}
              \href{{https://github.com/zjjc123}}{github.com/zjjc123}\\
              \href{{https://www.linkedin.com/in/zjjc123/}}{linkedin.com/in/zjjc123/}
          \end{flushright}
      \end{multicols}
  \end{center}
  %-----------HEADING-----------


  %-----------EDUCATION-----------
  \section{Education}
    \resumeSubHeadingListStart
      \resumeSubheading
        {University of Washington}{May 2025}
        {Computer Science B.S.}{Seattle, WA}
        \resumeItemListStart
          \resumeItem{3.84/4.0 GPA}
          \resumeItem{Relevant Coursework: Algorithms, Hardware Software Interface, Data Structures and Parallelism, Systems Programming, Database Management, Data Visualization, Machine Learning, Natural Language Processing}
        \resumeItemListEnd
    \resumeSubHeadingListEnd
  %-----------EDUCATION-----------


  %-----------EXPERIENCE-----------
  \section{Experience}

    \resumeSubHeadingListStart
      \resumeSubheading
        {Vial}{April 2024 - Present}
        {Software Engineer Intern}{Remote}
      \resumeItemListStart
        \resumeItem{Led various projects as an intern developing multiple key features deployed to production.}
        \resumeItem{Migrated the user management system to Terraform and created automated pipelines for deployment.}
        
      \resumeItemListEnd

    
      \resumeSubheading
        {Optum}{June 2023 - September 2023}
        {AI Engineering Intern}{Remote}
      \resumeItemListStart
        \resumeItem{Facilitated the upload of millions of electronic health documents using AWS Serverless Application Model Stack.}
        \resumeItem{Designed and deployed data pipeline using AWS SAM, Cloud Formation, S3, Lambda, and EventBridge.}
      \resumeItemListEnd


      \resumeSubheading
        {University of Washington}{December 2022 - August 2023}
        {Research Assistant}{Seattle, WA}
      \resumeItemListStart
        \resumeItem{Used NLP to contextualize and analyze extensive biomedical data, including grant proposals, clinical notes, and safety reports.}
        \resumeItem{Applied state-of-the-art transformer models, and various supervised and unsupervised learning methods to medical data.}
      \resumeItemListEnd

      \resumeSubheading
        {Applied Hearing Science Lab}{December 2022 - August 2023}
        {Research Assistant}{Seattle, WA}
      \resumeItemListStart
        \resumeItem{Collaborated with UI Designers to seamlessly integrate impactful and user-friendly interfaces.}
        \resumeItem{Used React.js to develop accessible and dynamic UI for a novel self hearing aid fitting process.}
        \resumeItem{Created a Node.js server hosted on OpenMHA firmware to serve React app and communicate with the hearing aid firmware and settings.}
      \resumeItemListEnd

    \resumeSubHeadingListEnd
  %-----------EXPERIENCE-----------
  
  %-----------EVENTS-----------
  \section{Events and Awards}

    \resumeSubHeadingListStart
      \resumeSubheading
        {eBay ML Challenge 2022}{Novemeber 2022}
        {2nd place at eBay Competition}{Seattle, WA}
      \resumeItemListStart
        \resumeItem{Lead a team to place second place in the eBay ML Challenge 2022}
        \resumeItem{Trained robust NER models using transformers that classified various labels in product titles.}
      \resumeItemListEnd


      \resumeSubheading
        {Dubhacks ‘22 T-Mobile Track}{October 2022}
        {Most Marketable Award }{Seattle, WA}
      \resumeItemListStart
        \resumeItem{Won the Most Marketable Award by creating a Package Tracking Device using T-Mobile DevEdge IoT Developer Kit}
        \resumeItem{Wrote custom firmware code in C to collect and analyze data from various sensors.}
      \resumeItemListEnd

      \resumeSubheading
        {Jane Street ETC (Electronic Trading Challenge)}{July 2022}
        {Live simulated market making competition}{Seattle, WA}
      \resumeItemListStart
        \resumeItem{1st place in "Final Hour" scoring: \$1.5k total cash prize awarded to our team.}
        \resumeItem{Created the best trading and market-making bot to generate the most profit each round in a simulated market.}
      \resumeItemListEnd

    \resumeSubHeadingListEnd
  %-----------EVENTS-----------

  %-----------OPEN SOURCE-----------
  \section{Projects}

    \resumeSubHeadingListStart
      
      \resumeSubheading
        {\href{https://cse442.pages.cs.washington.edu/wi23/fp/turkey-syria-earthquake/}{Visualization: Turkiye-Syria Earthquakes}}{March 2022}
        {A story told through data visualization}{}
      \resumeItemListStart
        \resumeItem{Developed an interactive scrolling narrative visualization using React and D3.js}
        \resumeItem{Amplified the lesser-told story about the Turkiye-Syria Earthquakes that devastated the region in February of 2023.}
        \resumeItem{Constructed various animated maps, bar charts, and other visualization techniques. Won best overall presentation in UW CSE 442 Wi.}
      \resumeItemListEnd

      \resumeSubheading
        {\href{https://pypi.org/project/guipylib/}{Guipy}}{May 2022}
        {A python UI open-sourced library}{}
      \resumeItemListStart
        \resumeItem{Founded a pygames UI components library that allows users to quickly create graphical interfaces.}
        \resumeItem{Created automatic polishing and version tagging with GitHub Action.}
      \resumeItemListEnd

    \resumeSubHeadingListEnd
  %-----------Projects-----------

  %-----------SKILLS-------------
  \section{Technologies} 

    \begin{itemize}[leftmargin=0in, label={}]
        \item {
          \resumeItemListStart
            \resumeItem{\textbf{Languages:} C++, C\#, Java, Python, Rust, JavaScript, TypeScript.}
            \resumeItem{\textbf{Cloud:} GCP, Terraform, Azure SQL Databse, AWS Lambda, AWS S3, AWS EventBridge, AWS Cloud Formation}
            \resumeItem{\textbf{Data Science:} Transformers, Hugging Face, PyTorch, Pandas, NLTK, scikit-learn.}
            \resumeItem{\textbf{Database:} PostgreSQL, SQLite, Firebase Firestore.}
            \resumeItem{\textbf{Web Dev:} Node.js, React.js, Next.js, Tailwindcss, D3.js} 
            \resumeItem{\textbf{Misc:} Unity, Git, GitHub Actions, Docker, Unix, Figma}
            \resumeItem{\textbf{Media:} Adobe Photoshop, Adobe Lightroom, Adobe Premiere Pro, Davinci Resolve}
          \resumeItemListEnd
        }
    \end{itemize}
  %-----------SKILLS-------------
  
\end{document}